Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2023-01-09 paper.tex
Small edits from replying to reviewer 4

Allowing for continuous migration between the stem populations substantially
improved the fits relative to zero migration between stems ($LL \approx
-101,600$ vs. $-107,700$ in the merger model and $LL \approx -115,300$ vs.
$-126,500$ in the continuous migration model).  With continuous migration
between stems, population structure extends back to up to 1.5Ma
(Table~\ref{tab:migration-rates}).  Migration between the stems in these models
is moderate, with a fraction of migrant lineages each generation estimated as
$m=6.3\times10^{-5}-1.3\times10^{-4}$. For comparison, this is similar to
inferred migration rates between connected contemporary populations over the
past 50ka (Table~\ref{tab:migration-rates}). This ongoing (or at least,
periodic) gene flow qualitatively distinguishes these models from previously
proposed archaic hominin admixture models (Figure~\ref{fig:proposed-models}C)
as the early branches remain closely related, and each branch contributes large
amounts to all contemporary populations (Figure~\ref{fig:predictions}).
Because of this relatedness, only $1\%$ to $4\%$ of genetic differentiation
among contemporary populations can be traced back to this early population
structure (SI Section~\ref{sec:f4})

@@

Relative cross-coalescence rates (rCCR) have recently been used to estimate
divergence between a pair of populations, as measured by the rate of
coalescence between two groups divided by the mean within population
coalescence. Simulations of rCCR accuracy, however, focus on a ‘clean split’
between populations whereby groups diverge without subsequent gene flow.
Published estimates of the earliest human divergences with rCCR, which range
from 150ka-100ka \citep{Bergstrom2021-iw}, may be significantly biased when
compared to more complex models with gene flow as inferred here. We find that
midpoint estimates of rCCR are poor estimates for population divergence, often
underestimating divergence time by 50\% or greater (e.g., Mende vs. Gumuz
$\sim$15ka compared to a true divergence of 60ka), and recent migration can
lead to the misordering of divergence events (Figure~\ref{fig:validation}E). We
suggest that rCCR analyses which do not fit multiple parameters including gene
flow should be interpreted with caution.

@@

A population reticulation involves multiple stems contributing genetically to
the formation of a group. One way in which this can happen is through the
geographic expansion of one or both stems. For example, if during MIS 5, either
Stem 1S (Figure~\ref{fig:best-fit-models}B) from southern Africa moved
northward thereby encountering Stem 2, or Stem 2 moved from central/western
Africa southward into Stem 1S, then we could observe disproportionate
ancestry contributions from different stems in contemporary groups. We observed
two merger events. The first, between Stem 1S and Stem 2, resulted in the
formation of an ancestral Khoe-San population $\approx120$ka. The second event
$\approx100$ka between Stem 1E and Stem 2, resulted in the formation of the
ancestors of Eastern/Western Africans including the ancestors of ``Out of
Africans''. While $120$ka can be interpreted as the basal human population divergence,
we suggest concpetualizing this event as the time of most recent
shared ancestry among sampled populations.
``Population divergence'' in population genetics is a complex concept because 
of the co-estimation of divergence time and subsequent migration;
methods make differing assumptions regarding the degree of a ``clean'' split 
between descendant groups vs. isolation-with-migration 
(Figure ~\ref{fig:supp-rccr-data} and Figure~\ref{fig:supp-IM-misspecification}).
Therefore, wide variation exists in estimates of 
divergence time in the literature (e.g.\citep{Pagani2015-pz}).

>>>>

Allowing for continuous migration between the stem populations substantially
improved the fits relative to zero migration between stems ($LL \approx
-101,600$ vs.\ $-107,700$ in the merger model, Tables
\ref{tab:supp-merger-without-stem-migration} and
\ref{tab:supp-merger-with-stem-migration}, and $LL \approx -115,300$ vs.\
$-126,500$ in the continuous migration model, Tables
\ref{tab:supp-continuous-migration-no-mig} and
\ref{tab:supp-continuous-migration-no-mig}).  With continuous migration between
stems, population structure extends back to up to 1.5Ma
(Table~\ref{tab:migration-rates}).  Migration between the stems in these models
is moderate, with a fraction of migrant lineages each generation estimated as
$m=6.3\times10^{-5}-1.3\times10^{-4}$. For comparison, this is similar to
inferred migration rates between connected contemporary populations over the
past 50ka (Table~\ref{tab:migration-rates}). This ongoing (or at least,
periodic) gene flow qualitatively distinguishes these models from previously
proposed archaic hominin admixture models (Figure~\ref{fig:proposed-models}C)
as the early branches remain closely related, and each branch contributes large
amounts to all contemporary populations (Figure~\ref{fig:predictions}).
Because of this relatedness, only $1\%$ to $4\%$ of genetic differentiation
among contemporary populations can be traced back to this early population
structure (SI Section~\ref{sec:f4})

@@

Relative cross-coalescence rates (rCCR) have recently been used to estimate
divergence between a pair of populations, as measured by the rate of
coalescence between two groups divided by the mean within population
coalescence. Simulations of rCCR accuracy, however, focus on a ‘clean split’
between populations whereby groups diverge without subsequent gene flow.
Published estimates of the earliest human divergences with rCCR, which range
from 150ka-100ka \citep{Bergstrom2021-iw}, may be significantly biased when
compared to more complex models with gene flow as inferred here. We find that
midpoint estimates of rCCR are poor estimates for population divergence, often
underestimating divergence time by 50\% or greater (e.g., Mende vs.\ Gumuz
$\sim$15ka compared to a true divergence of 60ka), and recent migration can
lead to the misordering of divergence events (Figure~\ref{fig:validation}E). We
suggest that rCCR analyses which do not fit multiple parameters including gene
flow should be interpreted with caution.

@@

A population reticulation involves multiple stems contributing genetically to
the formation of a group. One way in which this can happen is through the
geographic expansion of one or both stems. For example, if during MIS 5, either
Stem 1S (Figure~\ref{fig:best-fit-models}B) from southern Africa moved
northward thereby encountering Stem 2, or Stem 2 moved from central/western
Africa southward into Stem 1S, then we could observe disproportionate
ancestry contributions from different stems in contemporary groups. We observed
two merger events. The first, between Stem 1S and Stem 2, resulted in the
formation of an ancestral Khoe-San population $\approx120$ka. The second event
$\approx100$ka between Stem 1E and Stem 2, resulted in the formation of the
ancestors of Eastern/Western Africans including the ancestors of ``Out of
Africans''. While $120$ka can be interpreted as the basal human population divergence,
we suggest concpetualizing this event as the time of most recent
shared ancestry among sampled populations.
``Population divergence'' in population genetics is a complex concept because 
of the co-estimation of divergence time and subsequent migration;
methods make differing assumptions regarding the degree of a ``clean'' split 
between descendant groups vs.\ isolation-with-migration 
(Figure ~\ref{fig:supp-rccr-data} and Figure~\ref{fig:supp-IM-misspecification}).
Therefore, wide variation exists in estimates of 
divergence time in the literature (e.g.\citep{Pagani2015-pz}).

### 2023-01-09 supplement.tex
Small edits from replying to reviewer 4

For each model tested, we ran multiple rounds of likelihood optimization, 
alternating between the \emph{optimize\_log\_fmin},
\emph{optimize\_log\_powell}, and \emph{optimize\_lbfgsb} methods to explore
parameter space and hone in on the best fit parameters. Initial guesses for
parameters were chosen from demographically plausible starting points and then
perturbed to explore space, using gradient descent (on the log of the
parameters). The best fits from these initial rounds of optimization were then
chosen as the starting points for optimization using the Powell and/or the
L-BFGS-B methods (as implemented in the SciPy optimization package
\citep{Virtanen2020-kr}). This process was repeated with alternating
optimization methods until the best fit parameter set converged consistently.

@@

\begin{table}[ht]
\caption{
    \label{tab:supp-continuous-migration}
    \textbf{Best-fit parameters from the Continuous-Migration model.}
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -115,280.
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & 95\% CIs\\
    \midrule
    $N_e$ & Ancestral effective population size & 6090 & 4180--6530 \\
    $N_{stem1}$ & Size of stem 1 lineage between Neanderthal and Nama splits & 8080 & 7130--8400 \\
    $N_{stem2}$ & Size of stem 2 lineage & 12340 & 11330--13580 \\
    $N_{Nama_0}$ & Initial Nama size & 11860 & 11160--12390 \\
    $N_{Nama_F}$ & Final Nama size & 221 & 215--226 \\
    $N_{MSL_0}$ & Initial Mende size & 9880 & 9500--10210 \\
    $N_{MSL_F}$ & Final Mende size & 27730 & 25930--28930 \\
    $N_{EA}$ & Size of East African branch & 7460 & 7270--7630 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3730 & 3560--3810 \\
    $N_{EP}$ & East African agriculturist size & 13110 & 12800--13290 \\
    $N_{GBR_0}$ & Initial British size & 951 & 940--981 \\
    $N_{GBR_F}$ & Final British size & 11874 & 11490--12090 \\
    $N_{Neand}$ & Neanderthal size & 2620 & 2380--27950 \\
    $T_{stems}$ & Stem split time (years) & 1223000 & 1199000--1382000 \\
    $T_{Nama}$ & Nama split time (years) & 134200 & 127800--139900 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $0.92\times10^{-5}$ & $0.41\times10^{-5}$--$1.43\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.11\times10^{-5}$ & $3.92\times10^{-5}$--$4.56\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $21.3\times10^{-5}$ & $21.2\times10^{-5}$--$21.8\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $4.16\times10^{-5}$ & $3.77\times10^{-5}$--$4.33\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $33.7\times10^{-5}$ & $33.0\times10^{-5}$--$36.3\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.642 & 0.639--0.656 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.255 & 0.245--0.263 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.155 & 0.151--0.160 \\
    $m_{stems}$ & Stem 1--stem 2 migration rate & $6.26\times10^{-5}$ & $6.14\times10^{-5}$--$7.83\times10^{-5}$ \\
    $m_{stem2-Nama}$ & Stem 2--Nama migration rate & $5.85\times10^{-5}$ & $4.50\times10^{-5}$--$7.04\times10^{-5}$ \\
    $m_{stem2-MSL}$ & Stem 2--Mende migration rate & $16.2\times10^{-5}$ & $13.8\times10^{-5}$--$18.9\times10^{-5}$ \\
    $m_{stem2-EA}$ & Stem 2--East Africa migration rate & $3.10\times10^{-5}$ & $2.18\times10^{-5}$--$3.65\times10^{-5}$ \\
    \bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{
    \label{tab:supp-merger-without-stem-migration}
    \textbf{Best-fit parameters from the Merger-Without-Stem-Migration model.}
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -107,694.
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & 95\% CIs\\
    \midrule
    $N_e$ & Ancestral effective population size & 10990 & 10100--11290 \\
    $N_{stem1}$ & Size of stem 1 lineage between stem 1--stem 2 split and stem 1E--stem 1S split & 278 & 113--606 \\
    $N_{stem2}$ & Size of stem 2 lineage & 27850 & 26500--35060 \\
    $N_{Nama_0}$ & Initial Nama and stem 1S size & 12640 & 11310--12910 \\
    $N_{Nama_F}$ & Final Nama size & 227 & 223--238 \\
    $N_{MSL_0}$ & Initial Mende size & 1190 & 10280--11630 \\
    $N_{MSL_F}$ & Final Mende size & 27440 & 25720--30180 \\
    $N_{EA}$ & Size of East African and stem 1E branch & 9016 & 8680--9140 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3440 & 3270--3470 \\
    $N_{EP}$ & East African agriculturist size & 13680 & 13120--13690 \\
    $N_{GBR_0}$ & Initial British size & 922 & 920--963 \\
    $N_{GBR_F}$ & Final British size & 12020 & 11790--12430 \\
    $N_{Neand}$ & Neanderthal size & 2100 & 1770--2110 \\
    $T_{stems}$ & Stem split time (years) & 400300 & 381400--410700 \\
    $T_{stem1}$ & Stem 1 split time into stem 1E and stem 1S (years) & 281600 & 154300--320400 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $0.229\times10^{-5}$ & $0.205\times10^{-5}$--$0.697\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.15\times10^{-5}$ & $3.90\times10^{-5}$--$4.42\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $19.9\times10^{-5}$ & $19.8\times10^{-5}$--$20.8\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $3.99\times10^{-5}$ & $3.34\times10^{-5}$--$3.95\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $35.5\times10^{-5}$ & $35.2\times10^{-5}$--$39.6\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.641 & 0.641--0.661 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.257 & 0.245--0.264 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.156 & 0.152--0.161 \\
    $m_{stems}$ & Stem 1--stem 2 migration rate & $0$ & fixed \\
    $T_{Nama}$ & Time of Nama merger event & 112300 & 101400--116800 \\
    $f_{stem 2 \rightarrow Nama}$ & Proportion of stem 2 ancestry making up initial Nama lineage ($1-f$ from stem 1S) & 0.731 & 0.706--0.769 \\
    $T_{EA}$ & Time of East Africa merger event & 95000 & 94500--101400 \\
    $f_{stem 2 \rightarrow EA}$ & Proportion of stem 2 ancestry making up initial East Africa lineage ($1-f$ from stem 1E) & 0.522 & 0.510--0.564 \\
    $T_{MSL}$ & Time of secondary admixture from stem 2 to Mende & 23510 & 22920--25510 \\
    $f_{stem 2 \rightarrow MSL}$ & Proportion of ancestry from secondary stem 2 admixture to Mende & 0.183 & 0.174--0.196 \\
    \bottomrule
\end{tabular}
\end{table}

>>>>

For each model tested, we ran multiple rounds of likelihood optimization,
alternating between the \emph{optimize\_log\_fmin},
\emph{optimize\_log\_powell}, and \emph{optimize\_lbfgsb} methods to explore
parameter space and hone in on the best fit parameters.  We imposed bounds on
many of the parameters in the fits (most of which did not hit the imposed
bounds). Population sizes had a lower bound of $N_e=100$, migration rates were
bounded between 0 and $10^{-3}$, and admixture proportions between 0 and 1.
Event times were only constrained to occur in the proper order (so that
populations were required to have positive existence times, for example).
Initial guesses for parameters were chosen from demographically plausible
starting points and then perturbed to explore space, using gradient descent (on
the log of the parameters). The best fits from these initial rounds of
optimization were then chosen as the starting points for optimization using the
Powell and/or the L-BFGS-B methods (as implemented in the SciPy optimization
package \citep{Virtanen2020-kr}). This process was repeated with alternating
optimization methods until the best fit parameter set converged consistently.

@@

\begin{table}[ht]
\caption{
    \label{tab:supp-continuous-migration}
    \textbf{Best-fit parameters from the Continuous-Migration model.}
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -115,280.
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & 95\% CIs\\
    \midrule
    $N_e$ & Ancestral effective population size & 6090 & 4180--6530 \\
    $N_{stem1}$ & Size of stem 1 lineage between Neanderthal and Nama splits & 8080 & 7130--8400 \\
    $N_{stem2}$ & Size of stem 2 lineage & 12340 & 11330--13580 \\
    $N_{Nama_0}$ & Initial Nama size & 11860 & 11160--12390 \\
    $N_{Nama_F}$ & Final Nama size & 221 & 215--226 \\
    $N_{MSL_0}$ & Initial Mende size & 9880 & 9500--10210 \\
    $N_{MSL_F}$ & Final Mende size & 27730 & 25930--28930 \\
    $N_{EA}$ & Size of East African branch & 7460 & 7270--7630 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3730 & 3560--3810 \\
    $N_{EP}$ & East African agriculturist size & 13110 & 12800--13290 \\
    $N_{GBR_0}$ & Initial British size & 951 & 940--981 \\
    $N_{GBR_F}$ & Final British size & 11874 & 11490--12090 \\
    $N_{Neand}$ & Neanderthal size & 2620 & 2380--2750 \\
    $T_{stems}$ & Stem split time (years) & 1223000 & 1199000--1382000 \\
    $T_{Nama}$ & Nama split time (years) & 134200 & 127800--139900 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $0.92\times10^{-5}$ & $0.41\times10^{-5}$--$1.43\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.11\times10^{-5}$ & $3.92\times10^{-5}$--$4.56\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $21.3\times10^{-5}$ & $21.2\times10^{-5}$--$21.8\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $4.16\times10^{-5}$ & $3.77\times10^{-5}$--$4.33\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $33.7\times10^{-5}$ & $33.0\times10^{-5}$--$36.3\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.642 & 0.639--0.656 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.255 & 0.245--0.263 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.155 & 0.151--0.160 \\
    $m_{stems}$ & Stem 1--stem 2 migration rate & $6.26\times10^{-5}$ & $6.14\times10^{-5}$--$7.83\times10^{-5}$ \\
    $m_{stem2-Nama}$ & Stem 2--Nama migration rate & $5.85\times10^{-5}$ & $4.50\times10^{-5}$--$7.04\times10^{-5}$ \\
    $m_{stem2-MSL}$ & Stem 2--Mende migration rate & $16.2\times10^{-5}$ & $13.8\times10^{-5}$--$18.9\times10^{-5}$ \\
    $m_{stem2-EA}$ & Stem 2--East Africa migration rate & $3.10\times10^{-5}$ & $2.18\times10^{-5}$--$3.65\times10^{-5}$ \\
    \bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{
    \label{tab:supp-merger-without-stem-migration}
    \textbf{Best-fit parameters from the Merger-Without-Stem-Migration model.}
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -107,694.
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & 95\% CIs\\
    \midrule
    $N_e$ & Ancestral effective population size & 10990 & 10100--11290 \\
    $N_{stem1}$ & Size of stem 1 lineage between stem 1--stem 2 split and stem 1E--stem 1S split & 278 & 113--606 \\
    $N_{stem2}$ & Size of stem 2 lineage & 27850 & 26500--35060 \\
    $N_{Nama_0}$ & Initial Nama and stem 1S size & 12640 & 11310--12910 \\
    $N_{Nama_F}$ & Final Nama size & 227 & 223--238 \\
    $N_{MSL_0}$ & Initial Mende size & 11190 & 10280--11630 \\
    $N_{MSL_F}$ & Final Mende size & 27440 & 25720--30180 \\
    $N_{EA}$ & Size of East African and stem 1E branch & 9016 & 8680--9140 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3440 & 3270--3470 \\
    $N_{EP}$ & East African agriculturist size & 13680 & 13120--13690 \\
    $N_{GBR_0}$ & Initial British size & 922 & 920--963 \\
    $N_{GBR_F}$ & Final British size & 12020 & 11790--12430 \\
    $N_{Neand}$ & Neanderthal size & 2100 & 1770--2110 \\
    $T_{stems}$ & Stem split time (years) & 400300 & 381400--410700 \\
    $T_{stem1}$ & Stem 1 split time into stem 1E and stem 1S (years) & 281600 & 154300--320400 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $0.229\times10^{-5}$ & $0.205\times10^{-5}$--$0.697\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.15\times10^{-5}$ & $3.90\times10^{-5}$--$4.42\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $19.9\times10^{-5}$ & $19.8\times10^{-5}$--$20.8\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $3.99\times10^{-5}$ & $3.34\times10^{-5}$--$3.95\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $35.5\times10^{-5}$ & $35.2\times10^{-5}$--$39.6\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.641 & 0.641--0.661 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.257 & 0.245--0.264 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.156 & 0.152--0.161 \\
    $m_{stems}$ & Stem 1--stem 2 migration rate & $0$ & fixed \\
    $T_{Nama}$ & Time of Nama merger event & 112300 & 101400--116800 \\
    $f_{stem 2 \rightarrow Nama}$ & Proportion of stem 2 ancestry making up initial Nama lineage ($1-f$ from stem 1S) & 0.731 & 0.706--0.769 \\
    $T_{EA}$ & Time of East Africa merger event & 95000 & 94500--101400 \\
    $f_{stem 2 \rightarrow EA}$ & Proportion of stem 2 ancestry making up initial East Africa lineage ($1-f$ from stem 1E) & 0.522 & 0.510--0.564 \\
    $T_{MSL}$ & Time of secondary admixture from stem 2 to Mende & 23510 & 22920--25510 \\
    $f_{stem 2 \rightarrow MSL}$ & Proportion of ancestry from secondary stem 2 admixture to Mende & 0.183 & 0.174--0.196 \\
    \bottomrule
\end{tabular}
\end{table}
